Natural Selection Across Three Generations of Americans

### 2024-02-20 hrs-selection.qmd
Residualised PGS on PCs then restandardized using sampling weights

@@

  form_pgs <- map(pgs, \(x) reformulate(c(x, pcs), response = "rlrs"))
  mod_pgs[[eth]] <- map(form_pgs, 
                               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_edyrs <- map(pgs, \(x) reformulate(c(x, pcs),
                                              response = "raedyrs"))
  mod_pgs_edyrs[[eth]] <- map(form_pgs_edyrs, 
                                     \(x) svyglm_quiet(x, r_eth))
  names(mod_pgs_edyrs[[eth]]) <- pgs

@@

  form_pgs_sibs <- map(pgs, 
                       \(x) reformulate(c(x, pcs), response = "r10sibs"))
  mod_pgs_sibs[[eth]] <- map(form_pgs_sibs,
                                    \(x) svyglm_quiet(x, r_parents_eth))

@@

    form_pgs_gkids <- map(pgs, 
                       \(x) reformulate(c(x, pcs), response = "rlrs_div_h13gkid"))
  mod_pgs_gkids[[eth]] <- map(form_pgs_gkids,
                                    \(x) svyglm_quiet(x, r_child_eth))

@@

  # the colon interaction estimates the effect separately within each group
  form_pgs_x_ed <- paste0(pgs, ":edu") |>
    map(\(x) reformulate(c(x, "edu", pcs), response = "rlrs"))
  mod_pgs_x_ed[[eth]]  <-
    map(form_pgs_x_ed, 
               \(x) svyglm_quiet(x, r_eth))

  tidy_pgs_x_ed[[eth]] <-
    map(mod_pgs_x_ed[[eth]], broom::tidy, conf.int = TRUE)
  names(tidy_pgs_x_ed[[eth]]) <- pgs
  tidy_pgs_x_ed[[eth]] <-
    list_rbind(tidy_pgs_x_ed[[eth]], names_to = "pgs") |>
    filter(!term %in% c("(Intercept)", "edu13-17", pcs)) |>
    mutate(edu = str_remove(term, ".*:"))

  form_pgs_x_inc <- paste0(pgs, ":income_med") |>
    map(\(x) reformulate(c(x, "income_med", pcs), response = "rlrs"))
  mod_pgs_x_inc[[eth]]  <-
    map(form_pgs_x_inc, 
               \(x) svyglm_quiet(x, r_eth))

  tidy_pgs_x_inc[[eth]] <-
    map(mod_pgs_x_inc[[eth]], broom::tidy, conf.int = TRUE)
  names(tidy_pgs_x_inc[[eth]]) <- pgs
  tidy_pgs_x_inc[[eth]] <-
    list_rbind(tidy_pgs_x_inc[[eth]], names_to = "pgs") |>
    filter(!term %in% c("(Intercept)", "income_medHigh", pcs)) |>
    mutate(income_med = str_remove(term, ".*:income_med"))

  form_pgs_x_mar <- paste0(pgs, ":married") |>
    map(\(x) reformulate(c(x, "married", pcs), response = "rlrs"))
  mod_pgs_x_mar[[eth]]  <-
    map(form_pgs_x_mar, 
               \(x) svyglm_quiet(x, r_eth))

  tidy_pgs_x_mar[[eth]] <-
    map(mod_pgs_x_mar[[eth]], broom::tidy, conf.int = TRUE)
  names(tidy_pgs_x_mar[[eth]]) <- pgs
  tidy_pgs_x_mar[[eth]] <-
    list_rbind(tidy_pgs_x_mar[[eth]], names_to = "pgs") |>
    filter(! term %in% c("(Intercept)", "marriedMarried", pcs)) |>
    mutate(
      married = str_remove(term, ".*:married")
    )

  form_pgs_x_agefb <- paste0(pgs, ":agefb") |>
    map(\(x) reformulate(c(x, "agefb", pcs), response = "rlrs"))
  mod_pgs_x_agefb[[eth]]  <-
    map(form_pgs_x_agefb, 
               \(x) svyglm_quiet(x, r_eth))

  tidy_pgs_x_agefb[[eth]] <-
    map(mod_pgs_x_agefb[[eth]], broom::tidy, conf.int = TRUE) |> 
    setNames(pgs) |> 
    list_rbind(names_to = "pgs") |>
    filter(! term %in% c("(Intercept)", "agefbHigh", pcs)) |>
    mutate(
      agefb = str_remove(term, ".*:agefb")
    ) 
}

@@

calc_eth_cor <- function (weights, data) {
  coef_pgs_white <- pgs |> 
        map(\(x) reformulate(c(x, pcs), response = "rlrs")) |> 
        map(\(x) lm(x, data, weights = weights, 
                    subset = ethnicity == "white")) |> 
        map2_dbl(pgs, \(x, y) coef(x)[[y]])
  coef_pgs_black <- pgs |> 
        map(\(x) reformulate(c(x, pcs), response = "rlrs")) |> 
        map(\(x) lm(x, data, weights = weights, 
                    subset = ethnicity == "black")) |> 
        map2_dbl(pgs, \(x, y) coef(x)[[y]])

@@

calc_cors_edu <- function (weights, data, var) {
  coef_pgs_fert <- pgs |> 
        map(\(x) reformulate(c(x, pcs), response = var)) |> 
        map(\(x) lm(x, data, weights = weights)) |> 
        map_dbl(\(x) coef(x)[[2]])

  coef_pgs_edu <- pgs |> 
        map(\(x) reformulate(c(x, pcs), response = "raedyrs")) |> 
        map(\(x) lm(x, data, weights = weights)) |> 
        map_dbl(\(x) coef(x)[[2]])

@@

calc_eth_diff <- function (weights, data) {
  coef_pgs_white <- pgs |> 
        map(\(x) reformulate(c(x, pcs), response = "rlrs")) |> 
        map(\(x) lm(x, data, weights = weights, 
                    subset = ethnicity == "white")) |> 
        map_dbl(\(x) coef(x)[[2]])
  coef_pgs_black <- pgs |> 
        map(\(x) reformulate(c(x, pcs), response = "rlrs")) |> 
        map(\(x) lm(x, data, weights = weights, 
                    subset = ethnicity == "black")) |> 
        map_dbl(\(x) coef(x)[[2]])

@@

f_resp <- map(pgs, \(x) reformulate(c(x, pcs), response = "raevbrn"))
f_sibs <- map(pgs, \(x) reformulate(c(x, pcs), response = "r10sibs"))

@@

f_resp <- map(pgs, \(x) reformulate(c(x, pcs), response = "rlrs"))
f_gkids <- map(pgs, \(x) reformulate(c(x, pcs), response = "rlrs_div_h13gkid"))

@@

  # "rlrs ~ pgs:term + term + pc1 + pc2 +..."
  forms <-  map(cross_terms, 
                \(x) reformulate(c(x, term, pcs), response = "rlrs"))
  mods <- map(forms, \(x) lm(x, data, weights = w))
  cfs <- map(mods, coef)
  cfs_low <- map_dbl(cfs, \(x) x[str_detect(names(x), low_group)])
  cfs_high <- map_dbl(cfs, \(x) x[str_detect(names(x), high_group)])

@@

form_pgs_control_agefb <- map(pgs, \(x) reformulate(c(x, "agefbn", pcs), 
                                                    response = "rlrs"))
mod_pgs_control_agefb <- map(form_pgs_control_agefb,
                             \(x) svyglm_quiet(x, rand, subset = 
                                                 ethnicity == "white"))
tidy_pgs_control_agefb <- map(mod_pgs_control_agefb, broom::tidy) |> 
                          list_rbind() |> 
                          filter(term %in% pgs)

@@

reg_simple <- lm(rlrs ~ scale(EA) ,rand$variables)
reg_pc <- lm(rlrs ~ scale(EA) + PC1_5A +PC1_5B +PC1_5C +PC1_5D +PC1_5E + 
             PC6_10A +PC6_10B +PC6_10C +PC6_10D +PC6_10E ,rand$variables)
# beta = -0.027651
reg_res_EA <- lm(`scale(EA)` ~ PC1_5A +PC1_5B +PC1_5C +PC1_5D +PC1_5E + 
             PC6_10A +PC6_10B +PC6_10C +PC6_10D +PC6_10E ,reg_pc$model)

@@

  # the colon interaction estimates the effect separately within each group
  form_pgs_x_ed <- paste0(pgs, "*edu") |>
    map(\(x) reformulate(c(x, "edu", pcs), response = "rlrs"))
  mod_pgs_x_ed[[eth]]  <-
    map(form_pgs_x_ed, 
               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_x_inc <- paste0(pgs, "*income_med") |>
    map(\(x) reformulate(c(x, "income_med", pcs), response = "rlrs"))
  mod_pgs_x_inc[[eth]]  <-
    map(form_pgs_x_inc, 
               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_x_mar <- paste0(pgs, "*married") |>
    map(\(x) reformulate(c(x, "married", pcs), response = "rlrs"))
  mod_pgs_x_mar[[eth]]  <-
    map(form_pgs_x_mar, 
               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_x_agefb <- paste0(pgs, "*agefb") |>
    map(\(x) reformulate(c(x, "agefb", pcs), response = "rlrs"))
  mod_pgs_x_agefb[[eth]]  <-
    map(form_pgs_x_agefb, 
               \(x) svyglm_quiet(x, r_eth))

@@

# some of the PGS have estimates rounded to zero and are thus useless
correct_scores <- filter(correct_scores, chip_h2 > 0, R2 > 0)

@@

correct_scores$twin_h2[correct_scores$pgs == "AFB"] <- 0.15
#correct_scores$twin_h2[correct_scores$pgs == "NEBwomen"] <- 0.28

####################################
# Calculating error corrected estimates
####################################

run_pgic_once <- function (pgs, r2, h2, h2_type) {
  pgic_command <- glue(
     'python3 pgi_correct/pgic.py --reg-data-file pgi_correct_data.txt', 
     '--outcome "rlrs" --pgi-var {pgs}',
     '--covariates "PC1_5A" "PC1_5B" "PC1_5C" "PC1_5D" "PC1_5E" "PC6_10A"',
     '"PC6_10B" "PC6_10C" "PC6_10D" "PC6_10E" --R2 {r2} --h2 {h2}',
     '--weights "weight"', 
     .sep = " ")
  system(pgic_command)

  # This removes "junk" rows in the way of our regression betas
  system("sed '1d;2d;3d;4d;5d;6d;7d;8d;9d' pgi_correct.res > reg_results")
  pgic_results <- readr::read_table("reg_results", col_names = TRUE,
                                    col_types = "cdddd")
  file.remove("reg_results")

  tibble(
    trait = pgs,
    beta  = pgic_results[[1, 4]],
    SE    = pgic_results[[1, 5]],
    Heritability = h2_type
  )
}

run_pgic_data <- function (score_data, h2_column, h2_type) {
  results <- map(1:nrow(score_data), 
    \(i) run_pgic_once(pgs = score_data$pgs[i], 
                       r2 = score_data$R2[i],
                       h2 = score_data[i, h2_column, drop = TRUE],
                       h2_type = h2_type)
  )

  list_rbind(results)
}

corrected_effects_snp <- run_pgic_data(correct_scores, h2_column = "chip_h2",
                                       h2_type = "Chip")
corrected_effects_twin <- run_pgic_data(correct_scores, h2_column = "twin_h2",
                                        h2_type = "Twin")

corrected_effects <- rbind(corrected_effects_snp, corrected_effects_twin)
corrected_effects$conf.low <- corrected_effects$beta - 1.96 *
                              corrected_effects$SE
corrected_effects$conf.high <- corrected_effects$beta + 1.96 *
                               corrected_effects$SE

unlink("pgi_correct_data.txt")

corrected_effects <- left_join(corrected_effects, correct_scores,
                               by = join_by(trait == Abr),
                               suffix = c("", ".y"))

# The odd looking results are for traits with large missing heritability e.g. Asthma. My guess is that the rare variants act somewhat differently as DHJ as argued, meaning traits with large missing heritability show nonsense twin heritability estimates.

@@

# Cleaning and saving corrected effects so people can have the exact figures
corrected_effects$TwinH2_Source <- corrected_effects$Source
corrected_effects |> 
  select(trait, beta, SE, Heritability, chip_h2, twin_h2, R2, 
           TwinH2_Source, PoldermanICF_ICD10_subchapter, Category) |> 
  readr::write_csv("Corrected_effects.csv")

@@

# TE Note that under Fisher's fundamental theorem of natural selection, the selection
# for fitness should be equal to it's heritability... But in HRS the
# the AFB PGS much more strongly predicts RLRS than the NEB PGS and it's selection
# is much lower than what the heritability of NEB should be.
# The low R2 of NEB causes it to be removed, but the genetics for NEB 
# could just be a little different in HRS versus other samples!
# NEB_result <-  corrected_effects-which(corrected_effects[,"trait"]=="NEBwomen"),]

corrected_effects |>
  # This removes ADHD due to the low power of the score. 
  # Note ADHD predict RLRS after bonferroni! 
  # It also removes NEB
  filter(R2 > 0.005) |> 
  mutate(
    trait = nice_names[trait],
    trait = fct_reorder(trait, beta)
  ) |>
  ggplot(aes(y = trait, x = beta, xmin = conf.low, xmax = conf.high,
           color = Heritability)) +
  geom_vline(xintercept = 0, color = "grey60") +
  geom_pointrange(aes(linetype = Heritability == "Twin"),
                  position = position_dodge(0.2)) +
  scale_linetype(guide = "none") +
  coord_cartesian(xlim = c(-0.3, 0.3)) +
  labs(x = "Corrected coefficient on RLRS", y = "") +
  theme_minimal() +
  facet_grid(Category ~ ., scales = "free_y", space = "free_y") +
  theme(strip.text.y = element_text(angle = -90,face = "bold"))

@@

  fs_fert <- map(pgs, \(x) reformulate(c(x, pcs), response = "rlrs"))
  fs_phen <- map(pgs, \(x) reformulate(c(x, pcs), response = phenotype))

>>>>

##############################################################
# Residualising then standardising PGS, with sampling weights
##############################################################

dat_eth_list <- list()

  r_eth <- rand |> subset(ethnicity == eth)

for (pg in pgs) {

  reg <- lm(get(pg) ~ PC1_5A + PC1_5B + PC1_5C + PC1_5D + PC1_5E +
                    PC6_10A + PC6_10B + PC6_10C + PC6_10D +PC6_10E, weights = weight, 
                    data = r_eth)

  r_eth <- r_eth |> mutate(
                    !!pg := get(pg) - predict(reg, r_eth),
                    mean_weight = mean(weight, na.rm=TRUE),
                    tot_weight = sum(weight, na.rm=TRUE),
                    mean_res_pgs = sum(get(pg)*weight, na.rm=TRUE)/tot_weight,
                    w.dev = weight*(get(pg) - mean_res_pgs)^2,
                    w.var.pgs = sum(w.dev, na.rm =TRUE)/tot_weight,
                    deman_pgs = get(pg) - mean_res_pgs,
                    !!pg := deman_pgs/sqrt(w.var.pgs)
  )
}

  dat_eth_list[[eth]] <- r_eth

}

rand <- dat_eth_list |> list_rbind()
pgs <- unique(c(pgs_white,pgs_black))

# SD of EA before and after this process goes from 1 to 1.01, implying that the HRS is slightly more diverse in EA than the population and that Z scoring using sampling weights doesn't really matter

@@

  form_pgs <- map(pgs, \(x) reformulate(c(x), response = "rlrs"))
  mod_pgs[[eth]] <- map(form_pgs, 
                               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_edyrs <- map(pgs, \(x) reformulate(c(x),
                                              response = "raedyrs"))
  mod_pgs_edyrs[[eth]] <- map(form_pgs_edyrs, 
                                     \(x) svyglm_quiet(x, r_eth))
  names(mod_pgs_edyrs[[eth]]) <- pgs

@@

  form_pgs_sibs <- map(pgs, 
                       \(x) reformulate(c(x), response = "r10sibs"))
  mod_pgs_sibs[[eth]] <- map(form_pgs_sibs,
                                    \(x) svyglm_quiet(x, r_parents_eth))

@@

    form_pgs_gkids <- map(pgs, 
                       \(x) reformulate(c(x), response = "rlrs_div_h13gkid"))
  mod_pgs_gkids[[eth]] <- map(form_pgs_gkids,
                                    \(x) svyglm_quiet(x, r_child_eth))

@@

  # the colon interaction estimates the effect separately within each group
  form_pgs_x_ed <- paste0(pgs, ":edu") |>
    map(\(x) reformulate(c(x, "edu"), response = "rlrs"))
  mod_pgs_x_ed[[eth]]  <-
    map(form_pgs_x_ed, 
               \(x) svyglm_quiet(x, r_eth))

  tidy_pgs_x_ed[[eth]] <-
    map(mod_pgs_x_ed[[eth]], broom::tidy, conf.int = TRUE)
  names(tidy_pgs_x_ed[[eth]]) <- pgs
  tidy_pgs_x_ed[[eth]] <-
    list_rbind(tidy_pgs_x_ed[[eth]], names_to = "pgs") |>
    filter(!term %in% c("(Intercept)", "edu13-17")) |>
    mutate(edu = str_remove(term, ".*:"))

  form_pgs_x_inc <- paste0(pgs, ":income_med") |>
    map(\(x) reformulate(c(x, "income_med"), response = "rlrs"))
  mod_pgs_x_inc[[eth]]  <-
    map(form_pgs_x_inc, 
               \(x) svyglm_quiet(x, r_eth))

  tidy_pgs_x_inc[[eth]] <-
    map(mod_pgs_x_inc[[eth]], broom::tidy, conf.int = TRUE)
  names(tidy_pgs_x_inc[[eth]]) <- pgs
  tidy_pgs_x_inc[[eth]] <-
    list_rbind(tidy_pgs_x_inc[[eth]], names_to = "pgs") |>
    filter(!term %in% c("(Intercept)", "income_medHigh")) |>
    mutate(income_med = str_remove(term, ".*:income_med"))

  form_pgs_x_mar <- paste0(pgs, ":married") |>
    map(\(x) reformulate(c(x, "married"), response = "rlrs"))
  mod_pgs_x_mar[[eth]]  <-
    map(form_pgs_x_mar, 
               \(x) svyglm_quiet(x, r_eth))

  tidy_pgs_x_mar[[eth]] <-
    map(mod_pgs_x_mar[[eth]], broom::tidy, conf.int = TRUE)
  names(tidy_pgs_x_mar[[eth]]) <- pgs
  tidy_pgs_x_mar[[eth]] <-
    list_rbind(tidy_pgs_x_mar[[eth]], names_to = "pgs") |>
    filter(! term %in% c("(Intercept)", "marriedMarried")) |>
    mutate(
      married = str_remove(term, ".*:married")
    )

  form_pgs_x_agefb <- paste0(pgs, ":agefb") |>
    map(\(x) reformulate(c(x, "agefb"), response = "rlrs"))
  mod_pgs_x_agefb[[eth]]  <-
    map(form_pgs_x_agefb, 
               \(x) svyglm_quiet(x, r_eth))

  tidy_pgs_x_agefb[[eth]] <-
    map(mod_pgs_x_agefb[[eth]], broom::tidy, conf.int = TRUE) |> 
    setNames(pgs) |> 
    list_rbind(names_to = "pgs") |>
    filter(! term %in% c("(Intercept)", "agefbHigh")) |>
    mutate(
      agefb = str_remove(term, ".*:agefb")
    ) 
}

@@

calc_eth_cor <- function (weights, data) {
  coef_pgs_white <- pgs |> 
        map(\(x) reformulate(c(x), response = "rlrs")) |> 
        map(\(x) lm(x, data, weights = weights, 
                    subset = ethnicity == "white")) |> 
        map2_dbl(pgs, \(x, y) coef(x)[[y]])
  coef_pgs_black <- pgs |> 
        map(\(x) reformulate(c(x), response = "rlrs")) |> 
        map(\(x) lm(x, data, weights = weights, 
                    subset = ethnicity == "black")) |> 
        map2_dbl(pgs, \(x, y) coef(x)[[y]])

@@

calc_cors_edu <- function (weights, data, var) {
  coef_pgs_fert <- pgs |> 
        map(\(x) reformulate(c(x), response = var)) |> 
        map(\(x) lm(x, data, weights = weights)) |> 
        map_dbl(\(x) coef(x)[[2]])

  coef_pgs_edu <- pgs |> 
        map(\(x) reformulate(c(x), response = "raedyrs")) |> 
        map(\(x) lm(x, data, weights = weights)) |> 
        map_dbl(\(x) coef(x)[[2]])

@@

calc_eth_diff <- function (weights, data) {
  coef_pgs_white <- pgs |> 
        map(\(x) reformulate(c(x), response = "rlrs")) |> 
        map(\(x) lm(x, data, weights = weights, 
                    subset = ethnicity == "white")) |> 
        map_dbl(\(x) coef(x)[[2]])
  coef_pgs_black <- pgs |> 
        map(\(x) reformulate(c(x), response = "rlrs")) |> 
        map(\(x) lm(x, data, weights = weights, 
                    subset = ethnicity == "black")) |> 
        map_dbl(\(x) coef(x)[[2]])

@@

f_resp <- map(pgs, \(x) reformulate(c(x), response = "raevbrn"))
f_sibs <- map(pgs, \(x) reformulate(c(x), response = "r10sibs"))

@@

f_resp <- map(pgs, \(x) reformulate(c(x), response = "rlrs"))
f_gkids <- map(pgs, \(x) reformulate(c(x), response = "rlrs_div_h13gkid"))

@@

  # "rlrs ~ pgs:term + term + pc1 + pc2 +..."
  forms <-  map(cross_terms, 
                \(x) reformulate(c(x, term), response = "rlrs"))
  mods <- map(forms, \(x) lm(x, data, weights = w))
  cfs <- map(mods, coef)
  cfs_low <- map_dbl(cfs, \(x) x[str_detect(names(x), low_group)])
  cfs_high <- map_dbl(cfs, \(x) x[str_detect(names(x), high_group)])

@@

form_pgs_control_agefb <- map(pgs, \(x) reformulate(c(x, "agefbn"), 
                                                    response = "rlrs"))
mod_pgs_control_agefb <- map(form_pgs_control_agefb,
                             \(x) svyglm_quiet(x, rand, subset = 
                                                 ethnicity == "white"))
tidy_pgs_control_agefb <- map(mod_pgs_control_agefb, broom::tidy) |> 
                          list_rbind() |> 
                          filter(term %in% pgs)

@@

reg_simple <- lm(rlrs ~ EA ,rand$variables)
reg_pc <- lm(rlrs ~ EA + PC1_5A +PC1_5B +PC1_5C +PC1_5D +PC1_5E + 
             PC6_10A +PC6_10B +PC6_10C +PC6_10D +PC6_10E ,rand$variables)
# beta = -0.027651
reg_res_EA <- lm(`scale(EA)` ~ PC1_5A +PC1_5B +PC1_5C +PC1_5D +PC1_5E + 
             PC6_10A +PC6_10B +PC6_10C +PC6_10D +PC6_10E ,reg_pc$model)

@@

  # the colon interaction estimates the effect separately within each group
  form_pgs_x_ed <- paste0(pgs, "*edu") |>
    map(\(x) reformulate(c(x, "edu"), response = "rlrs"))
  mod_pgs_x_ed[[eth]]  <-
    map(form_pgs_x_ed, 
               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_x_inc <- paste0(pgs, "*income_med") |>
    map(\(x) reformulate(c(x, "income_med"), response = "rlrs"))
  mod_pgs_x_inc[[eth]]  <-
    map(form_pgs_x_inc, 
               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_x_mar <- paste0(pgs, "*married") |>
    map(\(x) reformulate(c(x, "married"), response = "rlrs"))
  mod_pgs_x_mar[[eth]]  <-
    map(form_pgs_x_mar, 
               \(x) svyglm_quiet(x, r_eth))

@@

  form_pgs_x_agefb <- paste0(pgs, "*agefb") |>
    map(\(x) reformulate(c(x, "agefb"), response = "rlrs"))
  mod_pgs_x_agefb[[eth]]  <-
    map(form_pgs_x_agefb, 
               \(x) svyglm_quiet(x, r_eth))

@@

# some of the PGS have estimates rounded to zero and are thus useless
correct_scores <- filter(correct_scores, chip_h2 > 0, R2 > 0)
correct_scores <- correct_scores[,c("pgs",
                                    "chip_h2",
                                    "twin_h2",
                                    "R2",
                                    "Source", 
                                    "PoldermanICF_ICD10_subchapter",
                                    "Category")]

@@

correct_scores$twin_h2[correct_scores$pgs == "AFB"] <- 0.15
#correct_scores$twin_h2[correct_scores$pgs == "NEBwomen"] <- 0.28
pgs_correct <- correct_scores$pgs

####################################
# Running the regressions
####################################

form_pgs_correct <- map(pgs_correct, \(x) reformulate(c(x), response = "rlrs"))

corrected_effects <-  map(form_pgs_correct,  \(x) svyglm_quiet(x, rand)) |> 
    map(broom::tidy, conf.int = TRUE, conf.level = 0.95) |> 
    list_rbind() |>
    filter(term %in% pgs) |>
    rename(pgs = term) |>
    left_join(correct_scores)

corrected_effects_snp <- corrected_effects |>
    mutate(estimate = estimate*sqrt(chip_h2/R2),
           std.error = std.error*sqrt(chip_h2/R2),
           conf.low = conf.low*sqrt(chip_h2/R2),
           conf.high = conf.high*sqrt(chip_h2/R2),
           heritability = "Chip")

corrected_effects_twin <- corrected_effects |>
    mutate(estimate = estimate*sqrt(twin_h2/R2),
           std.error = std.error*sqrt(twin_h2/R2),
           conf.low = conf.low*sqrt(twin_h2/R2),
           conf.high = conf.high*sqrt(twin_h2/R2),
           heritability = "Twin")

corrected_effects <- rbind(corrected_effects_snp, corrected_effects_twin)

@@

corrected_effects <- corrected_effects |> 
  rename(trait = pgs,
         TwinH2_Source = Source,
         Heritability = heritability)

corrected_effects |>
  select(trait, estimate, std.error, Heritability, chip_h2, twin_h2, R2, 
           TwinH2_Source, PoldermanICF_ICD10_subchapter, Category) |> 
  readr::write_csv("Corrected_effects.csv")

@@

corrected_effects |>
  # This removes ADHD due to the low power of the score. 
  # Note ADHD predict RLRS after bonferroni! 
  # It also removes NEB
  filter(R2 > 0.005) |> 
  mutate(
    trait = nice_names[trait],
    trait = fct_reorder(trait, estimate)
  ) |>
  ggplot(aes(y = trait, x = estimate, xmin = conf.low, xmax = conf.high,
           color = Heritability)) +
  geom_vline(xintercept = 0, color = "grey60") +
  geom_pointrange(aes(linetype = Heritability == "Twin"),
                  position = position_dodge(0.2)) +
  scale_linetype(guide = "none") +
  coord_cartesian(xlim = c(-0.3, 0.3)) +
  labs(x = "Corrected coefficient on RLRS", y = "") +
  theme_minimal() +
  facet_grid(Category ~ ., scales = "free_y", space = "free_y") +
  theme(strip.text.y = element_text(angle = -90,face = "bold"))

@@

  fs_fert <- map(pgs, \(x) reformulate(c(x), response = "rlrs"))
  fs_phen <- map(pgs, \(x) reformulate(c(x), response = phenotype))
